Manuscript draft

### 2019-06-03 manuscript/manuscript draft.Rmd
updated manuscript draft

@@

Primary productivity of forests is influenced by a range of factors. On a local scale, stand age [@Litton2007; @Gillman2015], management [@Simova2017]; nutrient availability [cite]; and altitude [@Girardin2010; @Malhi2017] all impact stand productivity. On a global scale, changes in primary productivity are influenced by climatic variables and abiotic gradients, such as the length of growing season [@Michaletz2014]. The majority of studies to date have focused on the influence of MAP and MAT on productivity. While MAP and MAT have been argued to be significant predictors of productivity [@Chu2016], other studies have found that the correlation between productivity and MAT is a factor of the relationship between productivity and growing season length [@Kerkhoff2005; @Malhi2012; @Michaletz2014; @Michaletz2018]. The influence of other climate variables on global patterns of productivity remains under-explored.

>>>>

Little is known about the main environmental drivers of these patterns.

@@

Primary productivity of forests is influenced by a range of factors. On a local scale, stand age [@Litton2007; @Gillman2015], management [@Simova2017]; nutrient availability [@Aragao2009]; and altitude [@Girardin2010; @Malhi2017] all impact stand productivity. On a global scale, changes in primary productivity are influenced by climatic variables and abiotic gradients, such as the length of growing season [@Michaletz2014]. The majority of studies to date have focused on the influence of MAP and MAT on productivity. While MAP and MAT have been argued to be significant predictors of productivity [@Chu2016], other studies have found that the correlation between productivity and MAT is a factor of the relationship between productivity and growing season length [@Kerkhoff2005; @Malhi2012; @Michaletz2014; @Michaletz2018]. The influence of other climate variables on global patterns of productivity remains under-explored.
